Finch: Sparse and Structured Array Programming with Control Flow

### 2024-04-02 sections/related.tex

Many libraries support BLAS plus a few sparse array types, typically CSR, CSC, BCSR, and COO.
%
Examples include Scipy, PETSc, Armadillo, and Eigen~\cite{virtanen2020scipy, abhyankarpetsc, Rumengan2021, eigenweb}.

>>>>

Many libraries support BLAS plus a few sparse array types, typically CSR, CSC, BCSR, and COO.
%
Examples include Scipy, PETSc, Armadillo, and Eigen~\cite{virtanen2020scipy, abhyankarpetsc, Rumengan2021, eigenweb}.
%
Several of these libraries also feature some graph or mesh algorithms built on sparse matrices.
%
GraphBlas exemplifies this pattern with support for many sparse matrix operations on a variety of formats~\cite{kepner2016mathematical} although a variety of other graph libraries adopt a similar approach such as LAgraph or GBase~\cite{mattson2019lagraph, kang2011gbase} among many others.
